\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-12-01 tex/paper.tex
Added some equations that might or might not be correct

@@

\fix Picture of the front-end

@@

\subsubsubsection{API}
In this work a RESTful API was implemented and used for back-end $\Leftrightarrow$ front-end
communication.

>>>>

\begin{itemize}
    \item[] c - Container
        \subitem Represents a structure that symbolises a folder in a virtual file system
    \item[] f - File
        \subitem A file in the system 
    \item[] p - Pointer
        \subitem A pointer to a file in the system 
    \item[] u - User
        \subitem A user in the system
    \item[] a - Access property
        \subitem Granted access to container
    \item[] A[u,c] - Access matrix
        \subitem Describes what containers the users in the system can access 
\end{itemize}

\subsection{Access rights}
\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } p \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\fix Picture of the newest front-end
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.4]{frontend.png}}
    \caption{Front-end~\cite{BTRFS}}
    \label{fig:frontend}
\end{figure}

@@

\subsubsubsection{API}
In this work a RESTful API was implemented and used for back-end $\Iff$ front-end
communication.
